---
title       : Fuel Consumption Estimator
subtitle    : MPG Estimator based on transmission type, car weight, HP and number of cylinders
author      : J-G Blouin
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Introduction

An application calculating gas consumption per mile is proposed.
The user must select

* Transmission type
* Number of cylinders
* Car weight (in 1000 lbs)
* Horse Power

A confidence interval can be selected, indicating a requested precision.

---
## How it works

Caluculations are based on a linear model approximation relating MPG 
to the selected variables. The model thus built is then used for interpolation.
The Result tab contains 
* the estimated value for MPG called fit 
* the lower bound for the confidence interval, called lwr
* the upper bound for the confidence interval, called upr

The Plot tab contains a representation of the confidence interval.  

The model is given by
```{r, echo= TRUE}
fit <- lm(mpg ~ factor(am) + wt + factor(cyl) + hp, data=mtcars)
```

---
## The Data

The data used to define the model comes from the mtcvars data set and looks like

```{r, echo= FALSE}
data(mtcars)
head(mtcars)
fit <- lm(mpg ~ factor(am) + wt + factor(cyl) + hp, data=mtcars)
```
where am is the transmission type:
* 0 for automatic
* 1 for manual

---

## The Model Summarized

The residual standard error is given by
```{r, echo= FALSE}
summary(fit)$sigma
```
The F-statistic is given by
```{r, echo= FALSE}
summary(fit)$fstatistic
```
The multiple R-squared and adjusted R-squared are given respectively by
```{r, echo= FALSE}
summary(fit)$r.squared
summary(fit)$adj.r.squared
```
And, lastly, the p-value is approximately null.